### 2022-01-09 cleave.tex
andresa fixes

For the purpose of this work, we have used \ac{CLEAVE} to implement an emulated \emph{inverted pendulum} control loop; see \cref{fig:invpend}.
We have chosen this system as an initial benchmark for to its relative simplicity as well as prevalence in the field of automatic control as one of the fundamental examples of linear control.
However, we eventually plan to build an open library of emulated control loops to be able to provide more thorough and varied benchmarks.

>>>>

For the purpose of this work, we have used \ac{CLEAVE} to implement an emulated \emph{inverted pendulum} control loop; see \cref{fig:invpend}.
We have chosen this system as an initial benchmark for its relative simplicity as well as prevalence in the field of automatic control as one of the fundamental examples of linear control.
However, we eventually plan to build an open library of emulated control loops to be able to provide more thorough and varied benchmarks.

### 2022-01-09 conclusion.tex
andresa fixes

The issue of repeatable and scalable benchmarks has been largely glossed over in \ac{NCS} literature; existing research is mostly focused on \emph{theory}, and the small fraction of experimental research studies available tend to implement \emph{ad-hoc} solutions.
To the best of our knowledge, \textcite{Zoppi2020NCSBench}'s work is the only available framework for \ac{NCS} benchmarking with repeatability and reproducibility in mind.

In this work, we aim to tackle this issue by presenting a fully software-based framework for repeatable, reproducible, and easily scalable \ac{NCS} benchmarking with a particular focus on edge deployment.
Our framework, \ac{CLEAVE}, is fully parametrizable and built with industry-standard edge technologies and paradigms in mind.
We validate the utility of this tool through a series of scenarios, from which we are able to extract relevant metrics relating to the stability of the control system, as well as on the perfomance of the underlying network link.
We believe \ac{CLEAVE} represents an impor-
tant step towards enabling inexpensive and low-complexity
scalable research for real-world deployment of edge-bound \acp{NCS}.

There is still however work to be done.
To start with, the current implementation of \ac{CLEAVE} only includes a single plant-controller pair.
We envision creating an open library of plants and controllers to share with the community.

\ac{CLEAVE}'s integration with industry-standard tools and frameworks such as Docker will be refined.
At the moment, these interactions are still quite superficial.
Our goal is to achieve a much tighter integration, for instance by providing the complete toolkit as pre-packaged container images.

Finally, the validity of the results obtained by the framework will have to be verified through more thorough and realistic scenarios than what we have been able to show in this work.
In particular, we intend to eventually perform large-scale experimentation targetting 5G cellular deployments, as this technology is set to become the backbone of edge networks in the near future.

>>>>

The issue of repeatable and scalable benchmarks has been largely glossed over in \ac{NCS} literature; existing research is mostly focused on \emph{theory}, and the small fraction of experimental research studies available tend to implement \emph{ad-hoc} solutions.
To the best of our knowledge, the work by \textcite{Zoppi2020NCSBench} is the only available framework for \ac{NCS} benchmarking focused on repeatability and reproducibility.

In this work, we aim to tackle this issue by presenting a fully software-based framework for repeatable, reproducible, and easily scalable \ac{NCS} benchmarking with a particular focus on edge deployment.
Our framework, \ac{CLEAVE}, is fully parametrizable and built with industry-standard edge technologies and paradigms in mind.
We validate the utility of this tool through a series of scenarios, from which we are able to extract relevant metrics relating to the stability of the control system, as well as on the perfomance of the underlying network link.
\todo[inline]{Talk a bit more about results?}
We believe \ac{CLEAVE} represents an important step towards enabling inexpensive and low-complexity scalable research for real-world deployment of edge-bound \acp{NCS}.

There is still, however, work to be done.
To start with, the current implementation of \ac{CLEAVE} only includes a single plant-controller pair.
We envision creating an open library of plants and controllers to share with the community.
\ac{CLEAVE}'s integration with industry-standard tools and frameworks such as Docker will be refined.
At the moment, these interactions are still quite superficial.
Our goal is to achieve a much tighter integration, for instance by providing the complete toolkit as pre-packaged container images.
Finally, the validity of the results obtained by the framework will have to be verified through more thorough and realistic scenarios than what we have been able to show in this work.
In particular, we intend to eventually perform large-scale experimentation targetting 5G cellular deployments, as this technology is set to become the backbone of edge networks in the near future.

### 2022-01-09 experiments.tex
andresa fixes

We repeat each combination of these parameters at least \num{10} times, for both the networked and ``local-only'' setups; experiments with interesting and relevant results are then repeated an additional \num{20} times for better statistical significance in the results.
Each repetition lasts for \SI{5}{\minute}, during which we collect detailed data on both the state of the controlled system as well as on the data sent over the network.

@@

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable collection and posterior processing of relevant metrics.  
\Cref{fig:single:stability} shows the results relating to the stability of the plants in the single-loop scenarios:
\cref{fig:single:topple} shows a visualization of the fraction of plants that toppled in each scenario, and \cref{fig:single:rms} shows the average \ac{RMS} amplitude for the pendula angles.
We identify toppled plants simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value depends on the parametrization of the controller; in this case it corresponds to \SI{0.35}{\radian}.} were marked as ``toppled''.

@@

For completeness, we also showcase \ac{CLEAVE}'s ability to obtain network performance data from the experiments.
\Cref{fig:single:rtt} shows average latency due to network and processing (excluding synthetic delays) for both single-loop scenarios.
Packet losses were below \SI{0.2}{\percent} for all parametrizations of the single-loop scenario over the network, and \SI{0}{\percent} for all parametrizations of the local-only setup.

@@

\Cref{fig:video:results} shows a summary of the results obtained from the realistic scenario.
These results are interesting in their counter-intuitiveness.
Conventional wisdom would lead us to think that higher sampling rates are always better for the stability of control systems; however, \cref{fig:video:toppled,fig:video:rms} clearly shows this not to be the case for \ac{NCS} in resource-constrained scenarios.
\SI{60}{\hertz} was the least stable configuration, with at least one pendulum toppling in around \SI{16}{\percent} of the repetitions, and average pendulum angle \ac{RMS} about \num{3} times that of the \SI{40}{\hertz} scenario.
\SI{40}{\hertz} was in turn the second worst configuration --- although no pendula toppled in this scenario, average angle \ac{RMS} were double that of the \SI{20}{\hertz} setup.

>>>>

We repeat each combination of these parameters at least \num{10} times, for both the networked and ``local-only'' setups; experiments with interesting and relevant results are then repeated an additional \num{20} times for better statistical significance in the results.
\todo[inline]{Explain criteria for repeated experiments? Or just drop this sentence?}
Each repetition lasts for \SI{5}{\minute}, during which we collect detailed data on both the state of the controlled system as well as on the data sent over the network.

@@

We begin with a simple analysis of the stability of the Plant, as \ac{CLEAVE} allows for straightforward and repeatable collection and posterior processing of relevant metrics.  
\cref{fig:single:stability} shows the results relating to the stability of the plants in the single-loop scenarios:
\cref{fig:single:topple} shows a visualization of the fraction of plants that toppled in each scenario, and \cref{fig:single:rms} shows the average \ac{RMS} amplitude for the pendula angles.
We identify toppled plants simply by analyzing the emulation data --- instances whose pendulum angles reached values above a certain value\footnote{This value depends on the parametrization of the controller; in this case it corresponds to \SI{0.35}{\radian}.} were marked as ``toppled''.

@@

For completeness, we also showcase \ac{CLEAVE}'s ability to obtain network performance data from the experiments.
\cref{fig:single:rtt} shows average latency due to network and processing (excluding synthetic delays) for both single-loop scenarios.
Packet losses were below \SI{0.2}{\percent} for all parametrizations of the single-loop scenario over the network, and \SI{0}{\percent} for all parametrizations of the local-only setup.

@@

\cref{fig:video:results} shows a summary of the results obtained from the realistic scenario.
These results are interesting in their counter-intuitiveness.
Conventional wisdom would lead us to think that higher sampling rates are always better for the stability of control systems; however, \cref{fig:video:toppled,fig:video:rms} clearly shows this not to be the case for \ac{NCS} in resource-constrained scenarios.
\SI{60}{\hertz} was the least stable configuration, with at least one pendulum toppling in around \SI{16}{\percent} of the repetitions, and average pendulum angle \ac{RMS} about \num{3} times that of the \SI{40}{\hertz} scenario.
\SI{40}{\hertz} was in turn the second worst configuration --- although no pendula toppled in this scenario, average angle \ac{RMS} were double that of the \SI{20}{\hertz} setup.

### 2022-01-09 intro.tex
andresa fixes

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in later years.
However, this rapid increase in adoption of these systems has been mostly limited to industrial contexts.
Although \acp{CPS} present huge opportunities for all facets of society, they have yet to reach our daily lives in any relevant scale due to their stringent operational requirements.
This is about to change, however, as with the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing~\cite{Satya2009Case,Satya2017Emergence}, consumer-grade \acp{CPS} will be made possible.
These technologies meet two key requirements of \acp{CPS}: real-time capabilities (through extremely low end-to-end latencies), and context- and locality-awareness, and will most likely become the backbone of \ac{CPS} in the future.

@@

% These systems have been of great interest to the scientific community in the last decade.
Due to their potential advantages for industrial and commercial settings~\cite{Lu2015WSAN}, a large body of work exists dedicated to the modelling and performance characterization of \aclp{NCS}~\cite{Hespanha2007Survey,Zhang2013Survey,Zhang2016Survey}.
\Acp{NCS} enhance the flexibility of and improve existing control systems by allowing for the distribution of control functions over and across networks.
This allows for --- for instance --- simultaneous centralized coordination, control, and monitoring of potentially hundreds of devices.

>>>>

The number and applications of \acp{CPS}~\cite{Rajkumar2010CPS} --- that is, systems in which a real, physical mechanism is controlled by a computer --- have exploded in recent years.
However, this rapid increase in adoption of these systems has been mostly limited to industrial contexts.
Although \acp{CPS} present huge opportunities for all facets of society, they have yet to reach our daily lives in any relevant scale due to their stringent operational requirements.
This is about to change, however, as with the advent of novel wireless communication technologies as well as networking paradigms, such as cellular 5G and Edge (and Fog) Computing~\cite{Satya2009Case,Satya2017Emergence}, consumer-grade \acp{CPS} will be made possible.
These technologies meet two key requirements of \acp{CPS}: real-time capabilities (through extremely low end-to-end latencies), and context- and locality-awareness, and will most likely become the backbone of \ac{CPS} in the future.

@@

% These systems have been of great interest to the scientific community in the last decade.
Due to their potential advantages for industrial and commercial settings~\cite{Lu2015WSAN}, a large body of work exists dedicated to the modelling and performance characterization of \aclp{NCS}~\cite{Hespanha2007Survey,Zhang2013Survey,Zhang2016Survey}.
\Acp{NCS} enhance the flexibility of and improve existing control systems by allowing for the distribution of control functions over and across networks.
This allows for, for instance, simultaneous centralized coordination, control, and monitoring of potentially hundreds of devices.
